The impact of cosmic variance on simulating weak lensing surveys

### 2014-10-22 Writeup/paper_v3.tex
single stellar population conversation

%Alternatively, we can impose cuts on stellar mass of the galaxies instead of imposing on the luminosity. 
%If we restrict to galaxies with masses $M$ such that $\log(M/M_\odot) \ge 10.15$, then we have at least {\bf 95.0\% } completeness.
Finally, we can circumvent the problem of redshift evolution of the
luminosity by imposing cuts on stellar mass instead. In Fig.~\ref{fig:smf}, we show the stellar mass function (SMF) of our sample for various F814W flux limits.
\cite{Tomczak_SMF} report the SMFs for the ZFOURGE survey, which
includes COSMOS. They considered for this work a single stellar
population (\rachel{What do you mean by a single stellar population?} \arun{I had lifted that term from the paper since I thought it was important to highlight that. 
They consider those stars that have metallicity of that of the sun formed at redshift $z=5$.})
following a Chabrier IMF \citep{ChabrierIMF}. 
We plot their SMF for \emph{all} galaxies in Fig.~\ref{fig:smf} for
reference. Their SMF is higher than ours since they reach a $K_s$-band
$5\sigma$ depth of 24.9. 
As for $M_I$, we compare the stellar mass function in the $m_\text{F814W}\le23.5$ sample with that in the $m_\text{F814W}\le25.2$ sample. 
The sample with $\log(M/M_\odot) > 10.15$ is $\sim 95$ per cent
complete in the redshift bin $0.75 \le z< 0.85$ and has 10~341
galaxies in total across all redshifts.
Thus, we construct a third volume-limited sample \s$3$ by imposing the stellar mass cut mentioned above. The number of galaxies in redshift slices
are tabulated in Table~\ref{table:GalaxyCounts} for all three ways
discussed in this section for obtaining a volume-limited sample. The
stellar-mass limited sample is the smallest, most likely because when
converting from flux to stellar mass, the stellar mass-to-light ratios
vary strongly with galaxy type, so red galaxies with high $M_*/L$
simply have too low a flux compared to the blue galaxies at the same
$M_*$, and are not observed.

>>>>

%Alternatively, we can impose cuts on stellar mass of the galaxies instead of imposing on the luminosity. 
%If we restrict to galaxies with masses $M$ such that $\log(M/M_\odot) \ge 10.15$, then we have at least {\bf 95.0\% } completeness.
Finally, we can circumvent the problem of redshift evolution of the
luminosity by imposing cuts on stellar mass instead. In Fig.~\ref{fig:smf}, we show the stellar mass function (SMF) of our sample for various F814W flux limits.
\cite{Tomczak_SMF} report the SMFs for the ZFOURGE survey, which
includes COSMOS. They calculated stellar masses using the procedure
and software described by \cite{2009ApJ...700..221K}, using a set of models
with exponentially declining star formation history \citep{2003MNRAS.344.1000B} assuming a
Chabrier IMF \citep{ChabrierIMF}.  (\rachel{What do you mean by a single stellar population?} \arun{I had lifted that term from the paper since I thought it was important to highlight that. 
They consider those stars that have metallicity of that of the sun
formed at redshift $z=5$.} \rachel{No, look more carefully: they used
that only to estimate completeness.  Their description of the stellar
mss estimation process says they used a set of BC03
models.  This would never work for a single population!  I left this
conversation here to correct this misimpression, but since I
fixed the text already, please remove this conversation once you've
read it - there are no further action items.}) 
We plot their SMF for \emph{all} galaxies in Fig.~\ref{fig:smf} for
reference. Their SMF is higher than ours since they reach a $K_s$-band
$5\sigma$ depth of 24.9. 
As for $M_I$, we compare the stellar mass function in the $m_\text{F814W}\le23.5$ sample with that in the $m_\text{F814W}\le25.2$ sample. 
The sample with $\log(M/M_\odot) > 10.15$ is $\sim 95$ per cent
complete in the redshift bin $0.75 \le z< 0.85$ and has 10~341
galaxies in total across all redshifts.
Thus, we construct a third volume-limited sample \s$3$ by imposing the
stellar mass cut mentioned above.

The number of galaxies in redshift slices
are tabulated in Table~\ref{table:GalaxyCounts} for all three ways
discussed in this section for obtaining a volume-limited sample. The
stellar-mass limited sample is the smallest, most likely because when
converting from flux to stellar mass, the stellar mass-to-light ratios
vary strongly with galaxy type, so red galaxies with high $M_*/L$
simply have too low a flux compared to the blue galaxies at the same
$M_*$, and are not observed.
